---
title: "Regression between residuals and terrain roughness"
author: "Yi Qiang"
date: "November 22, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
setwd("C:/Users/yiqi7710/work_CU/DistAdj/SAD_plotting")
library(knitr)
library(reshape2)
library(ggplot2)
library(RColorBrewer)
source("TM_residual.R")
```

## Correlation between residual and Terrain Ruggedness Index
###In each interval between two adjacent sample points
####Correlation between residuals along Transect 1 in Nebraska on

```{r eval=TRUE,echo=FALSE, fig.width = 15, fig.height = 10}
#Get RTI on 3m LiDAR data
benchmark=read.csv('C:/Users/yiqi7710/work_CU/data/Modified_2/Nebraska/sample_points/dist_tran1_res3.csv');
T_Indx=benchmark$DEM_ST;


path='C:/Users/yiqi7710/work_CU/data/Modified_2/Nebraska/sample_points/'

res_list=c(9,27,81,653);
med_list=c('ClosCtr','WeiAvg','BiLin','BiQua','BiCub','TIN','NN')

#Define empty matrices for correlation and regression coefficients
coef_L=matrix(, nrow = 4, ncol = 7);
sig_L=matrix(, nrow = 4, ncol = 7);
reg_coef_L=matrix(, nrow = 4, ncol = 7);
reg_ins_L=matrix(, nrow = 4, ncol = 7);
r_sqr_L=matrix(, nrow = 4, ncol = 7);
resids_L=matrix(list(),nrow = 4, ncol=7)
colnames(resids_L)=med_list
rownames(resids_L)=res_list

j=1;
for (med in med_list){
  i=1;
  
  par(mfrow=c(2,2),oma=c(2,2,2,2), mar=c(4,4,4,4))
  resids_res_L=list()
  for (res in res_list){
    in_file=paste0(path,'dist_tran1_res',res,'.csv'); #Specify the input file
    data=read.csv(in_file); #Read the csv file into matrix
    residual=abs(data[[j+9]]) #Extract the residuals of different methods
    
    #Plot scatterplots of residuals - T-Indx
    sub_title=paste0(res,"m resolution") #Define the title of sub-images in plot
    plot(T_Indx,residual, pch = 16, cex = 1,main=sub_title) #Create the scatterplot
    
    #Fit the residuals and T-Indx into a linear regression model
    lin_reg=lm(residual~T_Indx) #fit into a linear regression
    abline(lin_reg, col="red") # add regression line to the scatter plot
    lin_reg.sum=summary(lin_reg) #Get details of the regression model
    
    #Get the reg coef and R square
    reg_coef=lin_reg.sum$coefficients[1,2] #get reg coefficient
    intercept=lin_reg.sum$coefficients[1,1] #Get intercept
    r_square=lin_reg.sum$r.squared #Load r_sqr_L
      

    eq <- paste0("residual = ", round(intercept,5), ifelse(sign(round(reg_coef,5))==1, " + ", " - "), abs(round(reg_coef,5)), " T-Indx ")## sign check to avoid having plus followed by minus for negative coefficients
    mtext(eq, 3, line=0) # Add the equation to plot
    
    

    reg_coef_L[i,j]=reg_coef #Load regression coefficients into a matrix
    reg_ins_L[i,j]=intercept #Load intercept into a matrix
    r_sqr_L[i,j]=r_square #Load r_sqr_L
    
    coef_L[i,j]<-cor.test(residual, T_Indx)$estimate; #Load correlation coefficients into a matrix
    sig_L[i,j]<-cor.test(residual, T_Indx)$p.value; #Load correlation p value into a matrix
    
    #Get the residuals of the linear regression
    resids=lin_reg.sum$residuals
    resids_L[i,j]<-list(resids)
    
    #Define the column and row names of the matrices
    rownames(coef_L)=as.character(res_list);
    rownames(sig_L)=as.character(res_list);
    rownames(reg_coef_L)=as.character(res_list);
    rownames(r_sqr_L)=as.character(res_list);

    colnames(coef_L)=med_list;
    colnames(sig_L)=med_list;
    colnames(reg_coef_L)=med_list;
    colnames(r_sqr_L)=med_list;
    
    #Move the tick forward by 1
    i=i+1;
  }
  mtext(paste0('Method: ',med),line=0,side=3, outer=TRUE, cex=2)
  box(which = "outer", lty = "solid")
  j=j+1;
}
```

####Plot the correlation coefficents
```{r, echo=FALSE}
kable(coef_L, row.names = TRUE, col.names = colnames(coef_L))
```

####Plot the signicant level
```{r, echo=FALSE}
kable(sig_L, row.names = TRUE, col.names = colnames(coef_L))
```

####Plot the reggression coefficient
```{r, echo=FALSE}
#Create the table
kable(reg_coef_L, row.names = TRUE, col.names = colnames(coef_L))
```

```{r, echo=FALSE}
#Create the plot
matplot(reg_coef_L[,2:6], main="Regression coefficients", type = c("b"),lty=1, lwd=3,lend = 'butt', xaxt = "n", pch=1,col = brewer.pal(5, "Dark2")) #plot
legend("topleft", legend =med_list[2:6], col=brewer.pal(5, "Dark2"), pch=15, pt.cex=1.5 ,cex = 1.5) # optional legend
axis(1, at = c(1,2,3,4), labels = rownames(reg_coef_L), cex.axis = 1)
```

####Plot the R-Squares
```{r, echo=FALSE}
dev.off()
#Create the table
kable(r_sqr_L, row.names = TRUE, col.names = colnames(coef_L))
```

```{r, echo=FALSE}
#Create the plot
matplot(r_sqr_L[,2:6],main="R-Square", type = c("b"),lty=1, lwd=3,lend = 'butt', xaxt = "n", pch=1,col = brewer.pal(5, "Dark2")) #plot
legend("topleft", legend =med_list[2:6], col=brewer.pal(5, "Dark2"), pch=15, pt.cex=2 ,cex = 1.5) # optional legend
axis(1, at = c(1,2,3,4), labels = rownames(r_sqr_L), cex.axis = 1)

```


####Plot the R-square of the linear regression
```{r, echo=FALSE}
kable(r_sqr_L, row.names = TRUE, col.names = colnames(coef_L))
```

###Plot the line charts of all residuals
```{r, echo=FALSE}
TM_resids
```

###Plot the TM for residuals of different methods
```{r, echo=FALSE}
data1=read.csv(input_file)
resids=data1[10:20]
series=resids[1]
```